### 2017-06-29 motivation.tex
Edits.

>>>>

Let us now see how the above simple characterization of Postgres's RR
lets us verify \C{new\_order}. Firstly, since the database doesn't
change ($\Delta' = \Delta$) during the execution of the transaction's
body, we can reason about \C{new\_order} as if it is executing in
complete isolation until it is ready to commit. This reasoning is same
as the reasoning about sequential execution we performed earlier,
except that it now also includes a local state ($\delta$) that stores
local writes. Thus, when \C{new\_order} finishes execution and becomes
ready to commit, immediately flushing its local writes ($\delta$) to
the unchanged database state ($\Delta$) preserves the TPC-C invariant.
However, we are required to consider the  interference from concurrent
transitions at this point, which might change the database state from
$\Delta$ to $\Delta'$. If this interference includes the effects of a
concurrent \C{new\_order} transaction (with the same \C{d\_id}), then
verification fails as described previously
(Fig.~\ref{fig:new_order_execs}). Fortunately, we can show that this
is impossible; RR pre-empts a concurrent \C{new\_order} transaction
that modifies the same \C{District} record as the current transaction
(concretely, since the record is already present in current
transaction's $\delta$, transition from $\Delta$ to $\Delta'$ cannot
change this record). Thus \C{new\_order} preserves the TPC-C
invariant when executed under RR isolation on Postgres. Our proof
framework generalizes this style of reasoning to various isolation
levels on databases.

The second observation that informs our approach is one that pertains
to automation.
